---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(DBI)
knitr::opts_chunk$set(echo = FALSE)
```


## Let's create a data base

### Exercise 

In this scenario, we simulate a connection to a database.
We turn two pre-existing dataframes (mtcars and iris) into tables.
We will then use this database to practice our SQL.

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r dbCreation, exercise=TRUE}

# -------- Create a connection to the database "myDataBootcampDB"
# -------- We will use mydb to get access to the database
mydb <- dbConnect(RSQLite::SQLite(), "myDataBootcampDB.sqlite")


# -------- Ecriture des tables dans la base -------------
dbWriteTable(mydb, "mtcars", mtcars)
dbWriteTable(mydb, "iris", iris)



dbListTables(mydb)


```

```{r quiz}
quiz(
  question("What is the name of the tables created in the previous exercise?",
          answer("mtcar, iris", correct = TRUE),
          answer("myDataBootcampDB, mydb"),
          answer("myDataBootcampDB, mtcar, iris"),
          answer("myDataBootcampDB, iris, mydb, mtacr")
  )
)
```





## Let's query the database

You want to query the database using *SQL*.
To send a query to the database you need to use the dbGetQuery function.
The first parameter is the name of the connection. The second argument is a text string containing your SQL query.
dbGetQuery(**con**, **"your query"**)
Use the hint button if you need.

## a basic query

```{r query01-setup}

mydb <- dbConnect(RSQLite::SQLite(), "myDataBootcampDB.sqlite")
dbWriteTable(mydb, "mtcars", mtcars)
dbWriteTable(mydb, "iris", iris)
```

```{r query01, exercise=TRUE, exercise.lines = 5}
dbGetQuery(mydb, "----------")
```

```{r query01-hint-1}
print("Your SQL query should star by SELECT")
dbGetQuery(mydb, "SELECT")
```

```{r query01-hint-2}
print("SELECT is followed by the name of the columns (fields) you need. To get all the columns, use * ")
dbGetQuery(mydb, "SELECT *")
```

```{r query01-hint-3}
print("Next step is to stipulate the name of the table using the FROM statement ")
dbGetQuery(mydb, "SELECT * FROM")
```


```{r query01-solution}
dbGetQuery(mydb, "SELECT * FROM mtcars")
```



## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r eval=FALSE, include=FALSE}
# dbSendStatement(mydb, 'DROP TABLE mtcars')
# dbSendStatement(mydb, 'DROP TABLE iris')

# dbDisconnect(mydb)

```


